### 2016-06-23 sec7_experiment.tex
Revised section 5
fff
Revise Sec 5 last portion and Appendix

\section{Experimental Study}
\label{sec:exp}
In this section, we present our experimental findings on
deploying our GCMP detectors to large-scaled real trajectories.
All algorithms are were implemented in Java 1.7., and all the 
experiments are carried out on our in-house cluster: Dianwei. The cluster
includes 12 nodes, each of which has four quad-core 2.2GHz Intel processor,
32 GB memory and gigabit Ethernet. The cluster is installed with CentOS 5.5. 
operating system, Java 1.7.0 VM.

@@

spark.shuffle.spill & true \\ 

@@

\begin{table} [h]
\center
\small
\begin{tabular}{|l|l|l|l|}
\hline
 \textbf{Attributes}& \textbf{Geolife} & \textbf{ACTShopping} & \textbf{SingTaxi} \\ 
\hline 
\# objects & 18,670 & 13,183 & 15,054\\ 
\hline
\# average ts & 2,924 & 3,114 & 19,667 \\ 
\hline
\# data points & 54,594,696 & 41,052,242 & 296,075,837\\ 
\hline
\# snapshots & 10,699 & 16,931 & 44,364\\ 
\hline
\# clusters & 206,704 & 211,403 & 536,804\\
\hline
avg. cluster size & 223 & 171 & 484\\
\hline
\# of patterns & 441 & 369 & 585 \\
\hline
\end{tabular}
\caption{Statistics of data set}
\label{exp:dataset}
\end{table}

@@

\subsection{Effects of $G$ on GCMP}
\begin{figure*}[t]
\centering
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{exp/effectiveness/effect_geolife.eps}
        \caption{Geolife}
    \end{subfigure}
    \begin{subfigure}[b]{0.33\textwidth}
        \includegraphics[width=\textwidth]{exp/effectiveness/effect_shopping.eps}
        \caption{ACTShopping}
    \end{subfigure}
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{exp/effectiveness/effect_taxi.eps}
        \caption{SingTaxi}
    \end{subfigure}
\caption{Effectiveness of GCMP model on sampled datasets.}
\label{exp:effectiveness}
\end{figure*}
We first study the effects of introducing gap parameter $G$ on pattern discovery.
As shown in Figure~\ref{fig:related_work_scalability},
existing works are not able to handle large trajectories, 
we sample and cluster $1$ million trajectory points from the three real data.
We use two instances of GCMPs, GCMP-L where the $L$ value is default and GCMP where $L = 1$.  We measure the number
of patterns discvoered by different methods. The results are presented in Figure~\ref{exp:effectiveness}.

We can see from Figures~\ref{exp:effectiveness} that the number of patterns
discovered by GCMP is positively related to $G$. When $G =1$, the number
of patterns returned by GCMP and GCMP-L are identical to \emph{convoy}. As $G$ grows,
the number returned by GCMP-L converges to \emph{platoon}. For example, in (a), two
patterns converge when $G$ is $40$. Similarly in (b) and (c), two patterns converge
when $G$ is $50$. The reason is that when $G$ is large enough,
 all \emph{platoon}s are $G$-connected. Similar
 trend applies between GCMP and \emph{swarm}. As see from the figures, in (a), two
 patterns converge at $G=50$; while in (b) and (c) the two patterns converge
 at $G=60$ and $G=40$ respectively. We further
 note that, existing patterns has different granularity in temporal domain. As we seen
 from the three figures, the number of \emph{swarm} is greater than \emph{platoon} and
 \emph{convoy}. Despite none of the existing patterns are able to fine-grain control
 the temporal domain of patterns, GCMP can discover the patterns more precisely. 
 These results confirms the usefulness of GCMP in expressing other patterns.

\subsection{Performance Comparison}
%\textbf{Default Setting}: We now analyze the TRPM and SPARE algorithm under different
%parameter settings. Under the default parameter settings,
%the performance of TRPM and SPARE is shown as in the 
%following table:
%\begin{table}
%\small
%\begin{tabular}{|c|c|c|c|c|c|c|}
%\hline 
%Data Set& \multicolumn{2}{c|}{TRPM} & \multicolumn{2}{c|}{SPARE} & \# Patterns \\ 
%\hline 
% & Map-Shuffle & Reduce & Map-Shuffle & Reduce &  \\ 
%\hline 			
%Shopping &55 & 279 & 183 &414 &369\\ 
%\hline
%GeoLife &72 & 408 & 162 &585 &441  \\
%\hline
%Taxi &193 & 619 & 562 &3086 &585 \\
%\hline 
%\end{tabular} 
%\caption{Detail performance of TRPM and SPARE under default parameters.}
%\end{table}
%
%As can be seen from the above table, the number of patterns
%discovered by the default parameters are up to five hundreds.
%Thus, the parameter settings are reasonable. Besides, we 
%can see that TRPM suffers from shuffle and mining process. 
%This is because $\eta$ is set to be $309$ under default parameters.
%As a comparison, SPARE takes only in average
% 36\% of TRPM's shuffle time. 
To study the performance of TRMP and SPARE, we run both algorithms 
in all three datasets under different parameter settings. We report
their overall performance as in Figures~\ref{exp:performance_vary}.
In brief, both algorithms are able to handle the large-scaled real
datasets. However, we observe that TRMP's performance is very
dependent on the pattern parameters.
In cases when $G$ is large, TRMP takes near three hours (e.g., in Taxi dataset).
In contrast, SPARE performs quite stable. Another general observation
is that both algorithms run slower in the Taxi dataset as compared to in
other two datasets. This is because Taxi dataset contains
the most number of temporal data points, which is around 7 times of Shopping
dataset and 5 times of geolife dataset. We observe that, 
in almost all cases, SPARE outperforms TRMP and analyze the detail
of each scenario separately:

\textbf{Vary $M$}: Figures~\ref{exp:performance_vary} (a),(e),(i)
present the performance of TRPM and SPARE when $M$ changes under three datasets.
As the figures show, SPARE runs much faster than TRPM. We can see that SPARE
speeds up TRPM 2.7 times in Shopping data, 3.1 times in Geolife data and
7 times in Taxi data. Another observation is that, the running times
of both algorithms slightly decrease as $M$ grows. This is
because when $M$ becomes bigger, smaller clusters (stars) in 
the reduce phase of TRPM and SPARE can be directly pruned.

\textbf{Vary $K$}: Figure~\ref{exp:performance_vary} (b),(f),(j) 
presents the performance of TRPM and SPARE when $K$ changes under three datasets. 
There are two interesting findings in study the performance wrt. $K$. 
First, SPARE and TRPM takes different trends as $K$ increases. 
Whe $K$ increases, SPARE tends to have faster performances 
while TRPM's performances continuously slow down. For SPARE, the 
good performances result from more pruning powers brought
by $K$. When $K$ increases, many shorter time sequences in the reduce phase
are pruned. In contrast, $K$ does not bring much pruning power
during the reduce phase of TRPM. Even $K$ is very large, each reducers in TRPM
still has to sweep the entire partition to determine whether a pattern exists.
Moreover, $\eta$ in TRPM grows linearly with $K$. This indicates that
more data are shuffled and more snapshots are need to
be swept in each partition. This explains the low performance of TRPM as $K$
increases. Another interesting finding is that, when $K$ is small,
TRPM tends to outperform SPARE. This is because that when $K$ is small, shuffle
data of TRPM is comparable to SPARE. Meanwhile, small $K$ indicates small
size of partition in TRPM but low pruning power in SPARE. This explains the
superiority of TRPM. Note that, when $K$ is small, TRPM is at most 1.3 times
faster than SPARE and the absolute time is less than three minutes.

\textbf{Vary $L$}:Figure~\ref{} presents the performance
of TRPM and SPARE when $L$ changes under three datasets.

\textbf{Vary $G$}:Figure~\ref{} presents the performance
of TRPM and SPARE when $G$ changes under three datasets.

%\subsubsection{Effects of clusters $\epsilon$, minPt}

\begin{figure*}[t]
\centering
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_M.eps}
        \caption{Shopping Vary $M$}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_K.eps}
        \caption{Shopping Vary $K$}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_L.eps}
        \caption{Shopping Vary $L$}
    \end{subfigure}
       \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_G.eps}
        \caption{Shopping Vary $G$}
    \end{subfigure}

	\begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_M.eps}
        \caption{Geolife Vary $M$}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_K.eps}
        \caption{Geolife Vary $K$}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_L.eps}
        \caption{Geolife Vary $L$}
    \end{subfigure}
       \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_G.eps}
        \caption{Geolife Vary $G$}
    \end{subfigure}

    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_M.eps}
        \caption{Taxi Vary $M$}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_K.eps}
        \caption{Taxi Vary $K$}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_L.eps}
        \caption{Taxi Vary $L$}
    \end{subfigure}
       \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_G.eps}
        \caption{Taxi Vary $G$}
    \end{subfigure}       
\caption{Performance of SPARE and TRPM on real datasets under different pattern parameters.}
\label{exp:performance_vary}
\end{figure*}

\subsubsection{Effects of pattern parameters $M,L,K,G$}

\subsection{SPARE Analysis}
\subsubsection{Load Balance}
\subsubsection{Scalability}

>>>>

\section{Experimental Study}
\label{sec:exp}
In this section, we present our experimental findings on
deploying our GCMP detectors to large-scaled real trajectories.
All algorithms are were implemented in Java 1.7., and all the 
experiments are carried out on our in-house cluster: Dianwei. The cluster
includes 12 nodes, each of which is equipped with four quad-core 2.2GHz Intel processors,
32 GB memory and gigabit Ethernet. The cluster is installed with CentOS 5.5. 
operating system and Java 1.7.0 VM.

@@

@@

\begin{table} [h]
\center
\small
\begin{tabular}{|l|l|l|l|}
\hline
 \textbf{Attributes}& \textbf{ACTShopping} &  \textbf{Geolife} &  \textbf{SingTaxi} \\ 
\hline 
\# objects  & 13,183 & 18,670 & 15,054\\ 
\hline
\# average ts & 3,114  & 2,924 & 19,667 \\ 
\hline
\# data points  & 41,052,242 & 54,594,696 & 296,075,837\\ 
\hline
\# snapshots  & 16,931 & 10,699 & 44,364\\ 
\hline
\# clusters  & 211,403  & 206,704& 536,804\\
\hline
avg. cluster size  & 171 & 223 & 484\\
\hline
%\# of patterns & 3,741 & 4,369  & 7,585 \\
%\hline
\end{tabular}
\caption{Statistics of data set}
\label{exp:dataset}
\end{table}

@@

%\subsection{Effects of $G$ on GCMP}
%\begin{figure*}[t]
%\centering
%    \begin{subfigure}[b]{0.3\textwidth}
%        \includegraphics[width=\textwidth]{exp/effectiveness/effect_geolife.eps}
%        \caption{Geolife}
%    \end{subfigure}
%    \begin{subfigure}[b]{0.33\textwidth}
%        \includegraphics[width=\textwidth]{exp/effectiveness/effect_shopping.eps}
%        \caption{ACTShopping}
%    \end{subfigure}
%    \begin{subfigure}[b]{0.3\textwidth}
%        \includegraphics[width=\textwidth]{exp/effectiveness/effect_taxi.eps}
%        \caption{SingTaxi}
%    \end{subfigure}
%\caption{Effectiveness of GCMP model on sampled datasets.}
%\label{exp:effectiveness}
%\end{figure*}
%We first study the effects of introducing gap parameter $G$ on pattern discovery.
%As shown in Figure~\ref{fig:related_work_scalability},
%existing works are not able to handle large trajectories, 
%we sample and cluster $1$ million trajectory points from the three real data.
%We use two instances of GCMPs, GCMP-L where the $L$ value is default and GCMP where $L = 1$.  We measure the number
%of patterns discvoered by different methods. The results are presented in Figure~\ref{exp:effectiveness}.
%
%We can see from Figures~\ref{exp:effectiveness} that the number of patterns
%discovered by GCMP is positively related to $G$. When $G =1$, the number
%of patterns returned by GCMP and GCMP-L are identical to \emph{convoy}. As $G$ grows,
%the number returned by GCMP-L converges to \emph{platoon}. For example, in (a), two
%patterns converge when $G$ is $40$. Similarly in (b) and (c), two patterns converge
%when $G$ is $50$. The reason is that when $G$ is large enough,
% all \emph{platoon}s are $G$-connected. Similar
% trend applies between GCMP and \emph{swarm}. As see from the figures, in (a), two
% patterns converge at $G=50$; while in (b) and (c) the two patterns converge
% at $G=60$ and $G=40$ respectively. We further
% note that, existing patterns has different granularity in temporal domain. As we seen
% from the three figures, the number of \emph{swarm} is greater than \emph{platoon} and
% \emph{convoy}. Despite none of the existing patterns are able to fine-grain control
% the temporal domain of patterns, GCMP can discover the patterns more precisely. 
% These results confirms the usefulness of GCMP in expressing other patterns.
%  
%

\subsection{Performance Comparison}
Since the both TRPM and SPARE utlizes pruning rules that related to the 
pattern parameters $M$,$L$,$G$,$K$. It is interesting to
see the performance of TRPM and SPARE under different parameter settings.
%\textbf{Default Setting}: We now analyze the TRPM and SPARE algorithm under different
%parameter settings. Under the default parameter settings,
%the performance of TRPM and SPARE is shown as in the 
%following table:
%\begin{table}
%\small
%\begin{tabular}{|c|c|c|c|c|c|c|}
%\hline 
%Data Set& \multicolumn{2}{c|}{TRPM} & \multicolumn{2}{c|}{SPARE} & \# Patterns \\ 
%\hline 
% & Map-Shuffle & Reduce & Map-Shuffle & Reduce &  \\ 
%\hline 			
%Shopping &55 & 279 & 183 &414 &369\\ 
%\hline
%GeoLife &72 & 408 & 162 &585 &441  \\
%\hline
%Taxi &193 & 619 & 562 &3086 &585 \\
%\hline 
%\end{tabular} 
%\caption{Detail performance of TRPM and SPARE under default parameters.}
%\end{table}
%
%As can be seen from the above table, the number of patterns
%discovered by the default parameters are up to five hundreds.
%Thus, the parameter settings are reasonable. Besides, we 
%can see that TRPM suffers from shuffle and mining process. 
%This is because $\eta$ is set to be $309$ under default parameters.
%As a comparison, SPARE takes only in average
% 36\% of TRPM's shuffle time. 
%To study the performance of TRMP and SPARE, we run both algorithms 
%in all three datasets under different parameter settings. 
We run both of the two algorithms in all three dataset and report
their overall performances as in Figures~\ref{exp:performance_vary}.
In brief, both algorithms are able to handle the large-scaled real
datasets. However, we observe that TRMP's performance largely depends
on the pattern parameters. In cases when $G$ is large, 
TRMP takes near three hours (e.g., in Taxi dataset).
In contrast, SPARE performs quite stable. Another general observation
is that both algorithms run slower in the Taxi dataset as compared to
other two datasets. This is because Taxi dataset contains
the most number of temporal data points, which is around 7 times of Shopping
dataset and 5 times of geolife dataset. We observe that, 
in almost all cases, SPARE outperforms TRMP and analyze the detail
of each scenario separately.

\subsubsection{Effects of pattern parameters M,L,K,G}
\textbf{Vary $M$}: Figures~\ref{exp:performance_vary} (a),(e),(i)
present the performance of TRPM and SPARE when $M$ changes under three datasets.
As the figures show, SPARE runs much faster than TRPM. We can see that SPARE
speeds up TRPM 2.7 times in Shopping data, 3.1 times in Geolife data and
7 times in Taxi data. Another observation is that, the running times
of both algorithms slightly decrease as $M$ grows. This is
because when $M$ becomes bigger, smaller clusters (stars) in 
the reduce phase of TRPM and SPARE can be directly pruned.

\textbf{Vary $K$}: Figure~\ref{exp:performance_vary} (b),(f),(j) 
presents the performance of TRPM and SPARE when $K$ changes under three datasets. 
There are two interesting findings in study the performance wrt. $K$. 
First, SPARE and TRPM takes different trends as $K$ increases. 
Whe $K$ increases, SPARE tends to have faster performances 
while TRPM's performances continuously slow down. For SPARE, the 
good performances result from more pruning powers brought
by $K$. When $K$ increases, many shorter time sequences in the reduce phase
are pruned. In contrast, $K$ does not bring much pruning power
during the reduce phase of TRPM. Even $K$ is very large, each reducers in TRPM
still has to sweep the entire partition to determine whether a pattern exists.
Moreover, $\eta$ in TRPM grows linearly with $K$. This indicates that
more data are shuffled and more snapshots are need to
be swept in each partition. This explains the low performance of TRPM as $K$
increases. Another interesting finding is that, when $K$ is small,
TRPM tends to outperform SPARE. This is because that when $K$ is small, shuffle
data of TRPM is comparable to SPARE. Meanwhile, small $K$ indicates small
size of partition in TRPM but low pruning power in SPARE. This explains the
superiority of TRPM. Note that, when $K$ is small, TRPM is 30\% 
faster than SPARE and the absolute time is less than three minutes.

\textbf{Vary $L$}:Figures~\ref{exp:performance_vary} (c)(g)(k) presents the performance
of TRPM and SPARE when $L$ changes under three datasets. We can see that $L$
provides good pruning power from $10$ to $20$ for both TRPM and SPARE. For TRPM,
the benefit of increasing $L$ is bi-folded. First, when $L$ increases from $10-50$, 
the $\eta$ decreases, which reduces the shuffle and partition sizes. Second, when
$L$ increases, the initial pruning in line-sweep is more beneficial. For SPARE,
increasing $L$ does not affect the shuffling, but benefits the simplification.
It is also observed that when $L$ increases, the pruning power increases marginally.
This is because that many patterns contains short segments, when $L$ increases,
these patterns are largely pruned.

\textbf{Vary $G$}:Figures~\ref{exp:performance_vary} (d)(h)(l) presents the performance
of TRPM and SPARE when $G$ changes under three datasets. In general, both TRPM and SPARE
runs slower when $G$ increases. This is because, when $G$ increases, exponentially more valid patterns
exist. In other words, the pruning powers in TRPM and SPARE become weaker. We notice
that there is an burst of TRPM as $G$ increases. The major reason is that 
during line-sweep, if $G$-increases, each candidate needs to wait for more time before expiring.
This makes the candidate set exponentially grows and 
the join operation becomes very expensive.
Unlike TRPM, SPARE is although affected by the increase of $G$, 
but the impact is marginal as compared
to TRPM. This is because, although true patterns may become 
exponentially large as $G$ increases, the \emph{forward closure check} of SPARE
can quickly output true patterns without enumerating every of its subset.
%\subsubsection{Effects of clusters $\epsilon$, minPt}

\textbf{Number of patterns under different parameters}: Figures~\ref{exp:patterns_vary}
\begin{figure}[h]
\centering
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/effectiveness/patterns_vary_L.eps}
        \caption{Number of patterns vary $L$}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/effectiveness/patterns_vary_G.eps}
        \caption{Number of patterns vary $G$}
    \end{subfigure}    
\caption{Number of patterns discovered in three datasets on different parameters}
\label{exp:patterns_vary}
\end{figure}

\begin{figure*}[t]
\centering
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_M.eps}
        \caption{Shopping vary $M$}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_K.eps}
        \caption{Shopping vary $K$}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_L.eps}
        \caption{Shopping vary $L$}
    \end{subfigure}
       \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_G.eps}
        \caption{Shopping vary $G$}
    \end{subfigure}

	\begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_M.eps}
        \caption{Geolife vary $M$}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_K.eps}
        \caption{Geolife vary $K$}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_L.eps}
        \caption{Geolife vary $L$}
    \end{subfigure}
       \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_G.eps}
        \caption{Geolife vary $G$}
    \end{subfigure}

    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_M.eps}
        \caption{Taxi vary $M$}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_K.eps}
        \caption{Taxi vary $K$}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_L.eps}
        \caption{Taxi vary $L$}
    \end{subfigure}
       \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_G.eps}
        \caption{Taxi vary $G$}
    \end{subfigure}       
\caption{Performance of SPARE and TRPM on real datasets under different pattern parameters.}
\label{exp:performance_vary}
\end{figure*}

\subsubsection{Detail comparison between SPARE and TRPM}

\subsection{SPARE Analysis}

\subsubsection{Scalability}
\begin{figure}[h]
\centering
   \includegraphics[width=0.45\textwidth]{/exp/spare/scalability.eps}
\caption{Scalability of SPARE vary. $N$ under different datasets.}
\label{exp:patterns_vary}
\end{figure}

\subsubsection{Load Balance}
